### 2020-04-06 thesis_template/2_RelatedWork/model/spark.tex
knn debuggin

Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
This is result of dereferencing object with deallocation. Memory leak consumes more memory than necessary by making unreachable location.

@@

\section{Rust Memory Management}
\label{sec:history}
Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
In addition to characteristic of memory safety, this language also enables a developer to write concurrent code , fearless concurrency. 
Developers are able to write code with high performance given fair control of hardware and safety forced to follow restrictive pattern.

Main concepts of Memory Management in Rust are ownership, move, and borrowing. In ownership feature or Rust, each value has a variable called owner.
This owner has information about the value, such as location in memory, length and capacity of the value. This owner can live on the scope associated with its lifetime.
When the owner goes out of its scope, the value will be dropped. This feature is similar to how RAII in C++ works. 
However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.

With move, a value can be transferred from one owner to another, For example, a value is instantiated in a function. 
When it is returned to a new variable , the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.

Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
The reference goes out of scope, but ownership remains the same.

>>>>

Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.

@@

\section{Rust Memory Management}
\label{sec:history}
Rust is a system programming language which provides memory safety without runtime checking like GC and necessity of explicit memory de/allocation. 
To ensure memory safety, Rust provides restrictive coding patterns and checks lifetime of value and memory safety at compile-time.
The restrictive patterns also enables a developer to write fearless concurrent code that is free of data races.
Main concepts of Memory Management in Rust are ownership, move, and borrowing.

\subsection{Ownership}
In ownership feature or Rust, each value has a variable called owner.
This owner has information about the value, such as location in memory, length and capacity of the value. 
For example, the object representation of Vec$<$i32$>$ is shown in Figure. This owner can live on the scope associated with its lifetime.
When the owner is dropped, the value will be dropped too. This feature is similar to how RAII in C++ works. 
However, acquisition of owner out of the scope where it was constructed is available in Rust with the concept of move.

\subsection{Move}
In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
For example, a value is instantiated in a function. 
When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.

\subsection{Borrowing}
Borrowing lets code use a value temporarily without affecting its ownership so that it reduces unnecessary movement of ownership. 
One use case is when value is used in function and needed to be passed to the argument. If the argument takes ownership and the function does not return the value, 
the ownership of value goes out of scope and the memory is deallocated. One can pass reference of the value to the argument instead of owner. 
The reference goes out of scope, but ownership remains the same.
